### 2022-12-23 sections/experiments/_mitigation_strategies.qmd
merry xmas
uploaded real-world

### Mitigation Strategies

@@

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble,
]
generators = Dict(
    :Generic=>GenericGenerator(decision_threshold=0.5),
    :Latent=>REVISEGenerator(),
    :Generic_conservative=>GenericGenerator(decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(),
    :ClapROAR=>ClapROARGenerator()
)
```

#### Synthetic

@@

#### Plots

@@

##### Line Charts

@@

##### Error Bar Charts

@@

@@

@@

#### Latent Space Search

```{julia}
generators = Dict(
    :Latent=>GenericGenerator(decision_threshold=0.5),
    :Latent_conservative=>GenericGenerator(decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(),
    :ClapROAR=>ClapROARGenerator()
)
```

@@

#### Plots

##### Line Charts

@@

## Real World

>>>>

## Mitigation Strategies

@@

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble,
]
opt = Flux.Descent(0.01) 
generators = Dict(
    :Generic=>GenericGenerator(opt = opt, decision_threshold=0.5),
    :Latent=>REVISEGenerator(opt = opt),
    :Generic_conservative=>GenericGenerator(opt = opt, decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(opt = opt),
    :ClapROAR=>ClapROARGenerator(opt = opt)
)
```

### Synthetic

@@

### Plots

@@

#### Line Charts

@@

#### Error Bar Charts

@@

### Bootstrap

@@

### Chart in paper

@@

### Latent Space Search

```{julia}
generators = Dict(
    :Latent=>GenericGenerator(opt = opt, decision_threshold=0.5),
    :Latent_conservative=>GenericGenerator(opt = opt, decision_threshold=0.9),
    :Gravitational=>GravitationalGenerator(opt = opt),
    :ClapROAR=>ClapROARGenerator(opt = opt)
)
```

@@

### Plots

#### Line Charts

@@

### Real World

### 2022-12-23 sections/experiments/_synthetic.qmd
merry xmas
uploaded real-world

### Synthetic Data {#sec-app-synthetic}

@@

#### Experiment

@@

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble,
]
generators = Dict(
    :Greedy=>GreedyGenerator(), 
    :Generic=>GenericGenerator(),
    :REVISE=>REVISEGenerator(),
    :DICE=>DiCEGenerator(),
)
```

@@

#### Bootstrap

@@

#### Chart in paper {#sec-app-synthetic-paper}

@@

```{julia}
generate_artifacts(output_path)
generate_artifacts(www_path)
```

>>>>

## Synthetic Data {#sec-app-synthetic}

@@

### Experiment

@@

```{julia}
models = [
    :LogisticRegression, 
    :FluxModel, 
    :FluxEnsemble,
]
opt = Flux.Descent(0.01) 
generators = Dict(
    :Greedy=>GreedyGenerator(), 
    :Generic=>GenericGenerator(opt = opt),
    :REVISE=>REVISEGenerator(opt = opt),
    :DICE=>DiCEGenerator(opt = opt),
)
```

@@

### Bootstrap

@@

### Chart in paper {#sec-app-synthetic-paper}

@@

```{julia}
# generate_artifacts(output_path)
# generate_artifacts(www_path)
```
